\chapter{Conclusion \& Future Work}
\label{ch:conclusion}

% ------------------------------------------------------------------ Conclusion
\section{Conclusion}

This thesis presents an experimental validation of a kinematic-level \gls{tpc} framework specifically tailored for the Eelume robot. The primary contributions and findings of this research include:
\begin{itemize}
\item \textbf{Control, Visualization, and Simulation Software}: Comprehensive control, visualization, and simulation software was developed as part of this thesis. The control software facilitates efficient implementation and testing of task-priority controllers and other controller types without requiring detailed handling of low-level communication protocols. The visualization software provides immediate, real-time overviews of experimental results, while the simulation environment enables thorough and safe testing of experimental controllers prior to deployment on the actual Eelume robot.

\item \textbf{Low-level \gls{pd+} Controller}: A robust low-level \gls{pd+} controller was designed, implemented, and experimentally verified. The controller demonstrates reliable reference tracking, exhibiting some steady-state errors primarily in depth and roll orientations.

\item \textbf{Velocity-Level \gls{tpc}}: A velocity-level \gls{tpc} controller was successfully integrated into the control software and experimentally validated. This controller effectively tracks desired tasks and consistently respects task priority constraints when managing conflicting task objectives.

\item \textbf{Set-Based \gls{tpc}}: A velocity-level \gls{tpc} controller incorporating set-based tasks, designed specifically to handle joint limitations, was implemented and validated through experiments. The results confirmed reliable tracking performance under compatible task conditions and underscored the significance of careful task design when tasks become incompatible.
\end{itemize}

% ----------------------------------------------------------------- Future Work
\section{Future Work}
\label{sec:conclusion:future_work}

While this thesis demonstrates the feasibility of kinematic-level \gls{tpc} on a lightweight, highly redundant underwater robot, several areas remain open for further exploration and development. The work presented here lays the foundation for multiple extensions and improvements, both in terms of modeling accuracy and control strategy sophistication. Potential directions for future work include:

\begin{itemize}
    \item \textbf{Model identification}: Although an approximate dynamic model was developed as part of this thesis, further improvements are needed to enhance its fidelity. In particular, accurate estimation of added mass and hydrodynamic damping remains challenging. Dedicated experimental procedures could be designed to more precisely identify these parameters, significantly improving model-based control strategies.

    \item \textbf{Dynamic-level \gls{tpc}}: A natural extension of the work presented here is the implementation of \gls{tpc} at the dynamic level. This would require a significantly more accurate dynamic model, as control inputs would be computed based on full system dynamics rather than velocity kinematics alone. With a sufficiently precise model, dynamic-level TPC may offer improved performance in terms of responsiveness and disturbance rejection.

    \item \textbf{Controller tuning}: There is considerable scope for improving performance through systematic tuning of both the low-level \gls{pd+} controller and the high-level \gls{tpc} parameters. In particular, the proportional gains for individual tasks could be better adapted to system behavior. Additionally, since the robot's local dynamics vary with configuration, implementing a gain-scheduled or adaptive control strategy could further enhance tracking performance.

    \item \textbf{Rejection of joint measurement jitter}: Joint angle jitter was partially mitigated in this thesis using low-pass filtering. However, more advanced techniques—such as outlier detection, sensor fusion, or model-based filtering—could allow for more effective rejection of faulty measurements without introducing significant time delays.

    \item \textbf{Advanced control strategies}: The software and experimental framework developed in this thesis enables further research into advanced control techniques. Methods such as adaptive control, learning-based strategies, or alternative task-priority formulations could be implemented and tested using the same platform. This opens up new avenues for exploration and motivates continued development of the system.
\end{itemize}

