\chapter{Experimental Setup}

This chapter presents the experimental setup used to evaluate the task-
priority control framework developed in this thesis. It begins with an 
overview of the Eelume robot, including its mechanical structure, sensor suite
, communication systems, and suitability for underwater manipulation tasks. 
Following that, the software tools and interfaces used to control the robot 
and simulate its behavior are described. The chapter also outlines key 
assumptions and limitations in the experimental environment, including sensor 
noise and system constraints. Finally, the experimental procedures are detailed
, describing how specific robot behaviors will be tested and what kinds of 
responses are expected. Together, these sections provide the necessary context 
for understanding the practical validation of the proposed control approach.

% -----------------------------------------------------------------------------
\section{The Eelume Robot}

\begin{itemize}
    \item Model and Name
    \item DOF - joint-types, workspace dimensions
    \item Some kinematics
    \item sensor suite
    \item communication and battery
    \item TBS, water depth and wave influence
    \item Why it is so great for TPC
\end{itemize}

% -----------------------------------------------------------------------------
\section{Tools and software}
\begin{itemize}
    \item the Eelume low-level api over ethernet
    \item C/C++
    \item developed simulator and connection to Eely
    \item visualizer?
\end{itemize}

% -----------------------------------------------------------------------------
\section{Assumptions and Limitations}
\begin{itemize}
    \item navigation system (jittery angles and noisy velocities)
    \item frequency limitations
    \item no feedback on how slow/fast the lower-level controllers are
\end{itemize}

% -----------------------------------------------------------------------------
\section{Experimental Procedures}
\begin{itemize}
    \item show the response of the lower-level DP+ controller.
    \item Head + Tail stretching out
    \item Bending with joint constraints
    \item Expected results?
\end{itemize}
